\tightsection{Evaluation}

In this section, we evaluate the performance of the GO system. High level summary:

\tightsubsection{Setup}

We evaluate the performance on one content provider, short-form videos, iOS device (both iPhone and iPad), HLS protocol.
Adaptive bitrate switching algorithm from Apple player.

We evaluate two algorithms: random and optimized.

\tightsubsection{Rebuffering Rate and Average Bitrate}

\xi{florin's analysis on performance benefits}
\xi{show things do change and GO can react accordingly}

\tightsubsection{Adaptive Bitrate Stability}

\tightsubsubsection{When Do Bitrate Switching Happen?}

In this section, we empirically study when do bitrate switching happen. Figure XX shows when adaptive bitrate switch happen, where
x-axis is the percentage of actual video play time instead of content length. This is a conservative approach.

It shows that the majority of switches happen at 
the beginning of the video plays, i.e., X of the switches happen within Y of the video duration. 

\xi{we may add more algorithms if have time, also this may move from evaluation to previous sections since it is not really performance evaluation of algorithms.}

\tightsubsubsection{Reducing Number of Bitrate Switch}

Figure XX shows the number of bitrate switches for optimized and random decisions within the first minute. 
It shows that GO can reduce the number of switches.

\tightsubsubsection{Initial vs. Dominant Bitrate}

Figure XX shows the ratio of initial bitrate to dominant bitrate (1 is best). It shows that GO is close to dominant bitrate.
